\section*{\Large\centering \textbf{ABSTRACT}}
\addcontentsline{toc}{section}{Abstract}

This report presents the work carried out during the internship as a \textbf{Full Stack Web Developer} at \textbf{Information Care Pvt. Ltd.}. The internship was conducted with the objective of gaining practical exposure to full-stack application development, system architecture design, and modern web technologies in a professional environment.

During the internship period, various frontend and backend technologies were studied and implemented to design, develop, and maintain scalable web applications. On the frontend, responsive and user-centric interfaces were developed using modern JavaScript frameworks and component-based architecture principles. On the backend, RESTful APIs were designed and implemented with proper routing, authentication, and database integration to ensure secure and efficient data management.

Major activities included designing database schemas, implementing CRUD operations, integrating third-party APIs, managing authentication and authorization mechanisms, and optimizing application performance. The internship also involved version control using Git, collaborative development workflows, debugging, and deployment of applications to cloud environments.

In addition, tasks related to testing, performance optimization, and security enhancement were performed to ensure application reliability and robustness. Emphasis was placed on writing clean, maintainable code following industry best practices and software development lifecycle methodologies.

Overall, the internship provided practical knowledge of full-stack development, system integration, and real-world software engineering practices, helping to bridge the gap between academic learning and industry-level application development.

\small
\noindent \textbf{\textit{Keywords:}} Full Stack Development, Web Applications, Frontend, Backend, REST API, Database, Authentication, Deployment.
\newpage
