
\section*{\Large\centering \textbf{ACKNOWLEDGEMENT}}
\addcontentsline{toc}{section}{Acknowledgement}

First and foremost, I would like to express my sincere gratitude to \textbf{Kendrabindu Online Pvt. Ltd.}, Anamnagar, Kathmandu, for providing me with the opportunity to undertake my internship in the field of web development and system management. This internship offered valuable industry exposure and practical experience, helping me enhance my technical knowledge and professional skills in a real working environment.

I am deeply thankful to my supervisor and mentor at \textbf{Kendrabindu Online Pvt. Ltd.} for their continuous guidance, technical support, and encouragement throughout the internship period. Their mentorship played a significant role in strengthening my understanding of content management systems, database handling, web technologies, SEO practices, and server management.

I would also like to extend my sincere thanks to my supervisor, \textbf{Mr. Prakash Neupane}, for his support, constructive feedback, and supervision during the internship. His guidance greatly contributed to the successful completion of my assigned tasks and projects.


I would also like to extend my sincere appreciation to the faculty members of the \textbf{Department of Computer Science and Information Technology}, \textbf{Institute of Science and Technology (IoST)}, \textbf{Tribhuvan University}, for their academic guidance and support throughout my studies. Their knowledge and encouragement helped me successfully complete this internship.

I am grateful to my colleagues and team members at \textbf{Kendrabindu Online Pvt. Ltd.} for their cooperation and support during my internship. Their collaborative environment made this learning journey more effective and enjoyable.

Lastly, I would like to thank my family and friends for their constant support, motivation, and encouragement throughout this period.

Finally, I sincerely appreciate everyone who directly or indirectly contributed to making this internship a valuable and enriching learning experience.



\begin{flushright}
    \begin{tabular}{l}
        \textbf{ROHAN KHANAL [29604/078]}     \\       
    \end{tabular}
\end{flushright}

\newpage