\stepcounter{section}
\section*{\Large\centering {CHAPTER 3 \\ INTERNSHIP ACTIVITIES}}
\addcontentsline{toc}{section}{CHAPTER 3: Internship Activities}\label{3}

\subsection{Roles and Responsibilities}

During my internship at \textbf{Information Care Pvt. Ltd.}, I worked as a \textbf{Software Development Intern} in the full stack development team using the \textbf{PERN stack (PostgreSQL, Express.js, React.js, Node.js)}. My roles and responsibilities were aligned with structured software development practices and real-world business requirements.

\begin{itemize}

    \item Designed and developed dynamic web application features using React.js for frontend development.
    
    \item Developed RESTful APIs using Node.js and Express.js following proper route structuring and middleware usage.
    
    \item Designed and normalized PostgreSQL database schemas to maintain data integrity and reduce redundancy.
    
    \item Implemented CRUD operations across frontend, backend, and database layers.
    
    \item Applied separation of concerns by maintaining clear distinction between presentation layer, business logic layer, and data layer.
    
    \item Implemented JWT-based authentication and role-based authorization mechanisms.
    
    \item Managed asynchronous operations in backend services using async/await and proper error handling techniques.
    
    \item Performed input validation and structured error handling to enhance application reliability.
    
    \item Optimized SQL queries and improved API response performance.
    
    \item Used Git for version control and collaborative development.
    
    \item Participated in debugging, feature testing, and system improvement tasks.
    

    
\end{itemize}

\subsection{Weekly Log}

The following table provides a weekly breakdown of activities and tasks completed during the 12-week internship:

\begin{table}[H]
    \centering
    \caption{Weekly log of activities performed during the internship.}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{|c|p{13cm}|}

\hline
\textbf{Week} & \textbf{Activity Performed} \\
\hline

Week 1 & Introduction to company workflow, project requirements analysis, and development environment setup (Node.js, PostgreSQL, React, Next.js). \\
\hline

Week 2 & Understanding existing company website architecture and codebase; familiarization with React to Next.js migration strategy. \\
\hline

Week 3 & Migration of company website from React to Next.js; implementation of server-side rendering and routing structure. \\
\hline

Week 4 & Development of responsive frontend components for company website; implementation of modern UI design patterns. \\
\hline

Week 5 & Creation of user-reactive components and interactive UI elements; optimization of component rendering performance. \\
\hline

Week 6 & Introduction to Chiurika CMS project; requirement analysis and understanding of CMS architecture and functionality. \\
\hline

Week 7 & Implementation of CMS features for Chiurika website; development of content management interfaces and dynamic content rendering. \\
\hline

Week 8 & Database schema design for CMS content storage; integration of backend APIs with frontend CMS components. \\
\hline

Week 9 & Implementation of authentication and authorization for CMS admin panel; role-based access control for content management. \\
\hline

Week 10 & Integration and testing of complete CMS workflow; debugging and resolving frontend-backend integration issues. \\
\hline

Week 11 & UI/UX enhancement and responsiveness testing across devices; performance optimization and code refactoring. \\
\hline

Week 12 & Final testing, bug fixes, documentation preparation, and deployment support for both projects. \\
\hline

\end{tabular}
\end{table}

\subsection{Description of the Project Involved During Internship}

During my internship at \textbf{Information Care Pvt. Ltd.}, I was involved in two major projects: redesigning and migrating the company's official website from React to Next.js, and developing a Content Management System (CMS) for the Chiurika website.

\textbf{Project 1: Company Website Redesign and React to Next.js Migration}

The company website required modernization and migration from React.js to Next.js to leverage server-side rendering, improved performance, and SEO optimization. I analyzed the existing React codebase, planned the migration strategy, and executed the conversion of components to Next.js architecture. The migration involved converting client-side rendered pages to server-side rendered and static generated pages, implementing Next.js file-based routing, and optimizing the build process.

Following the migration, I focused on frontend development to create responsive and modern UI components. I designed and implemented reusable components with modern design patterns, ensuring consistent styling and functionality across all pages. Interactive UI elements were created using React hooks and state management, enabling dynamic user interactions. The components were optimized for performance, ensuring fast rendering and minimal re-renders. Cross-device testing was performed to ensure responsive design across desktop, tablet, and mobile platforms.

\textbf{Project 2: Chiurika CMS Development}

The Chiurika CMS project involved transforming the existing Chiurika website into a full-featured content management system. The project required designing and implementing a complete CMS workflow including content creation, editing, publishing, and management interfaces.

On the frontend, I developed the CMS admin panel with an intuitive user interface for content management. Key components included a content editor interface with rich text support, content listing and management pages, media upload and management functionality, and content preview and publishing features. The CMS was designed with role-based access control to restrict access to authorized users.

On the backend, I designed normalized PostgreSQL database schemas to store content, media files, and user information efficiently. RESTful APIs were implemented using Node.js and Express.js to handle CRUD operations for content management. Middleware functions were used for request validation, authentication verification, and structured routing. JWT-based authentication was implemented to secure the admin panel, ensuring that only authenticated users with appropriate roles could access content management features. Role-based authorization was applied to restrict specific operations based on user roles.

The development process followed structured software development lifecycle practices, including requirement analysis, system design, implementation, comprehensive testing, and deployment preparation. Version control using Git enabled collaborative development and maintained a complete history of changes.

\subsection{Activities Performed}

\begin{itemize}

\item \textbf{Website Migration and Architecture:}  
Analyzed existing React codebase, planned React to Next.js migration strategy, and executed component conversion with server-side rendering implementation.

\item \textbf{Responsive Frontend Development:}  
Designed and developed responsive React and Next.js components with modern UI patterns, ensuring consistent styling and functionality across all devices.

\item \textbf{Interactive UI Components:}  
Created user-reactive components with dynamic behavior, form validation, user feedback mechanisms, and optimized component rendering performance.

\item \textbf{CMS Admin Panel Development:}  
Implemented complete CMS admin interface including content editor, content listing, media management, and content publishing features.

\item \textbf{Backend API Development:}  
Designed and implemented RESTful APIs using Node.js and Express.js with proper middleware for validation, authentication, and structured routing.

\item \textbf{Database Design and Integration:}  
Designed normalized PostgreSQL schemas for CMS content storage, implemented database models and relationships, and optimized queries for performance.

\item \textbf{Authentication and Authorization:}  
Implemented JWT-based authentication for secure user session management and role-based access control for restricting CMS operations.

\item \textbf{Frontend-Backend Integration:}  
Integrated frontend CMS components with backend APIs, tested data flow, and resolved integration issues.

\item \textbf{Testing and Debugging:}  
Performed functional and integration testing of complete workflows, identified and fixed bugs, and ensured system reliability.

\item \textbf{Performance Optimization:}  
Optimized component rendering, API response times, SQL queries, and implemented code refactoring for maintainability.

\item \textbf{Cross-Device Testing and Responsiveness:}  
Conducted responsive design testing across desktop, tablet, and mobile platforms to ensure consistent user experience.

\item \textbf{Version Control and Collaboration:}  
Used Git for maintaining code history, managed code repositories, and facilitated collaborative development workflow.

\end{itemize}